---
title: "Assigment 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Below is the summary of the data set $\textit{gapminder}$, including key data, as well as an overview of the different countries belonging to the different continents using the $\texttt{table()}$ function.
```{r echo = FALSE}
library(gapminder)

summary(gapminder)

table(gapminder$continent)
```

Some features demonstrated:
  - Returning the first and last $$ elements of the object using the built in R function $\texttt{head()}$ and $\texttt{tail()}$.
  - Returning the number of columns and rows of the data set contains using the functions $\texttt{ncol()}$ and $\texttt{nrow()}$.
  - Returning the strucure of the object, using the function $\texttt{str()}$.

```{r echo=FALSE}
head(gapminder,10)
tail(gapminder,10)
ncol(gapminder)
nrow(gapminder)
str(gapminder)

```


Below we extract a specified column of the data set(lifeExp) and return the mean and the variance of it, using built in functions. 

```{r echo=FALSE}
lifeExp = gapminder$lifeExp
mean(lifeExp)
var(lifeExp)

```


Boxplot of the expected lifespan versus continent.

```{r echo = FALSE}
plot(lifeExp ~ continent, gapminder)
```

